Patchwork: Incremental Computation for Static Analysis

### 2019-01-22 paper.tex
Fill out incremental contribution sections

We developed an incremental data structure to represent the abstract states necessary to back our static analyses. It is...

@@

We use the discussed data structures in a modular framework for implementing static analyses. Our framework is organized as follows...

>>>>

We developed an incremental data structure to represent the abstract states necessary to back our static analyses. Our representation allows for efficient incremental joins to build up the underlying relation. We use the following naming strategy...

You are convinced (*wave hand*) that the data structures in question provides a unique performance improvement for our use case.

@@

We use the discussed data structures in a modular framework for implementing static analyses. Our framework requires the implementation of an abstract domain, including transfer function, to be given by the user. This approach allows us to take advantage of existing libraries used in the static analysis community. For this paper, we interfaced with APRON, an existing library supporting the numerical domains necessary for interval and octagon analysis. Once we have defined the language to operate on - in our case, Jimple - and the transfer function for our domain of choice (see examples), we can incrementally execute the analysis.

See figures 1/2 for an outline of the driving functions for the incremental analysis. By exploiting the structure of the typical 'worklist' algorithm for static analysis, we can achieve incremental performance gains.

Our naming strategy works by reference to (insert defense of naming strategy - strictly location?) (reference to analysis trace visualization - given by Benno in table 3)
